Writing News Captions with Bags of Attention

### 2019-10-27 paper/paper.tex
Add model parameter count

\begin{table*}[t]
	\caption {Model complexity: Number of trainable parameters}
	\label{tab:models}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Parameters \\
      \midrule
      GloVe + LSTM & 137M \\
      GloVe + Transformer & 148M \\
      RoBERTa + LSTM & 139M \\
      RoBERTa + Transformer & 154M \\
        + faces & 171M \\
		\bottomrule
	\end{tabular}
\end{table*}

>>>>

\begin{table*}[t]
	\caption {Model complexity: Number of trainable parameters}
	\label{tab:models}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Parameters \\
      \midrule
      GloVe + LSTM & 137M \\
      GloVe + Transformer & 148M \\
      RoBERTa + LSTM & 139M \\
      RoBERTa + Transformer & 154M \\
        + faces & 171M \\
        + names & 175M \\
        + faces + names & 192M \\
		\bottomrule
	\end{tabular}
\end{table*}
